### 2014-04-16 doc/uist14/interaction.tex
removed a dot
fixed two stage, four states

Our augmentation to Google Glass adds a 940nm 5mm IR emitter (SFH 4545 from OSRAM Opto Semiconductors Inc.). The emitter is controlled by an additional microcontroller which communicates with Google Glass through Bluetooth radio. (see Figure~\ref{fig:glass}). In the following description, we use the term ``Glass'' to refer to this augmented hardware.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/interactionModel2.pdf}
\caption{Four different states during the head-orientation targeting.}
\label{fig:interaction}
\end{figure}

>>>>

Our augmentation to Google Glass adds a 940nm 5mm IR emitter (SFH 4545 from OSRAM Opto Semiconductors Inc.). The emitter is controlled by an additional microcontroller which communicates with Google Glass through Bluetooth radio (see Figure~\ref{fig:glass}). In the following description, we use the term ``Glass'' to refer to this augmented hardware.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/interactionModel2.pdf}
\caption{Two main stages during the interaction with HOBS. For completeness, we have also show the final state of {\bf commit}.} 
\label{fig:interaction}
\end{figure}
